---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SpotifyProject

## Overview

The "SpotifyProject" package is an R package for utilizing Spotify's Web API for developers to pull information on a variety of topics, including artists, albums, tracks, and genres.  By just inputing an artist's name, you can gather a ton of fascinating data, including a summary of the artists danceability, valence, and energy, among many other measurements!

## Installation

```r
devtools::install_github("AdamDelRio/SpotifyProject")
```

## Authentication

Firstly, create an account [here](https://developer.spotify.com/my-applications/#!/applications) for the Spotify for Developers Web API.  After creating an account, create a dashboard, then check the settings for your client and secret id. 

Then, set both ids in your environment, as the function get_spotify_access_token() pulls these varaibles from the environment.  Alternatively, you can pass these varaibles into the function manually and store the returned string, but remember to include this new varible in all function calls.

```{r, eval = FALSE}
Sys.setenv(SPOTIFY_CLIENT_ID = "xxxxxxxxxxxxxxxxxxxxx")
Sys.setenv(SPOTIFY_CLIENT_SECRET = "xxxxxxxxxxxxxxxxxxxxx")
#OR
access_token <- get_spotify_access_token(SPOTIFY_CLIENT_ID = "xxxxxxxxxxxxxxxxxxxxx", 
                                         SPOTIFY_CLIENT_SECRET = "xxxxxxxxxxxxxxxxxxxxx")
```

## Usage

```{r}
Sys.setenv(SPOTIFY_CLIENT_ID = "9b791d794b834a379a7fb31fee32431d")
Sys.setenv(SPOTIFY_CLIENT_SECRET = "b582eccc019f4ab4aea3fdda49c0fb69")
```

### Which One Direction Member Is The Most Danceable?

```{r load_packages, message=FALSE, warning=FALSE, results="hide"}
library(SpotifyProject)
library(knitr)
library(tidyverse)
```

```{r, message = FALSE, warning = FALSE, results = 'asis'}
members <- get_artists_summary(queries = c("Harry Styles", "ZAYN", "Liam Payne", "Niall Horan", "Louis Tomlinson"))
members %>%
  dplyr::select(artist_name, danceability_mean) %>% 
  dplyr::arrange(desc(danceability_mean)) %>%
  dplyr::rename("Artist Name" = artist_name,
                "Mean Danceability" = danceability_mean) %>%
  kable(format = "markdown")
```

### How Loud Does "Bohemian Rhapsody" Get Throughout The Song?

```{r, message = FALSE, warning = FALSE, results = 'asis'}
rhap <- get_track_sections(query = "Bohemian Rhapsody")
rhap %>%
  dplyr::select(track_name,
                start,
                loudness) %>% 
  ggplot2::ggplot(mapping = aes(x = start, y = loudness)) + 
  ggplot2::geom_line() + 
  ggplot2::theme_bw() + 
  ggplot2::labs(title = "Loudness of Bohemian Rhapsody Over Time",
                subtitle = "Loudness (dB)",
                x = "Start Time of Interval (s)",
                y = "")
```

### Of The Top Hip-Hop Artists, Which 5 Have The Most Followers?

```{r, message = FALSE, warning = FALSE, results = 'asis'}
hop <- get_genre_artists(genre = "hip-hop")
hop %>% 
  dplyr::select(artist_name, 
                followers_total) %>% 
  dplyr::arrange(desc(followers_total)) %>% 
  dplyr::slice_head(n = 5) %>% 
  dplyr::rename("Artist Name" = artist_name, 
                "Total Followers" = followers_total) %>% 
  knitr::kable(format = "markdown")
```

### How Does The Average Valence, Energy, Speechiness, Danceability, And Acousticness Of Kendrick Lamar Compare To Ed Sheeran

```{r, message = FALSE, warning = FALSE, results = 'asis'}
create_average_artists_radar_chart(queries = c("Kendrick Lamar", "Ed Sheeran"), vars = c("danceability", "acousticness"))
```
